A Dataset of Operator-client Dialogues Aligned with Database Queries for End-to-end Training

### 2016-06-29 paper.tex
minor fix

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operator uses the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The~search interface is implemented in Javascript as a simple substring matching over values in the database.
We used such a simple interface because it is easy use for untrained CF workers.
Multiple constrains can be expressed by two substrings separated by a comma.
The content of the database is intentionally hidden.
If no filter value is specified, the operator does not see content of the database so the filter has to be used to answer clients questions.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.

>>>>

\vspace{-1.00em}
\subsection{Operator Interface}
\label{sec:operator}
The operator CF worker is asked to politely address the clients needs according to the information stored in the database.
In order to provide the information to clients, the operators use the simple database interface depicted in~Figure~\ref{fig:operator}:
They filter the restaurants using a full text search over the database.
The~search interface is implemented in Javascript as a simple substring matching over values in the database.
We used such a simple interface because it is easy use for untrained CF workers.
Multiple constrains can be expressed by two substrings separated by a comma.
The content of the database is intentionally hidden.
If no filter value is specified, the operator does not see content of the database so the filter has to be used to answer clients questions.
The CF workers are also instructed to explicitly mark the database rows to which they refer in their answer.
Similarly to the client role, the operator does not have to provide all requested information in a single turn.
It is left up to the~worker which information is provided first.
